\cvsection{学术论文}

\begin{cventries}
    \vspace{-1.5mm}
    \cvpapers
    {
        \begin{cvitems}
            \item {Xinze, Zhang, Junzhe Zhang, Zhenhua Chen, and Kun He. "Crafting Adversarial Examples for Neural Machine Translation." In Proceedings of the 59th Annual Meeting of the Association for Computational Linguistics (ACL), 2021. (CCF A, 计算机顶级会议，人工智能计算语言学Top 1)}
            \item {Xinze, Zhang, Kun He, and Yukun Bao. "Error-feedback stochastic modeling strategy for time series forecasting with convolutional neural networks." Neurocomputing, 2021, 459:234-248. (SCI A, IF 5.719, 30/139 Computer Science, Artificial Intelligence)}
            \item {Jianhua, Yang, Xinze, Zhang, and Yukun Bao, "Short-term Load Forecasting of Central China based on DPSO-LSTM," In Proceedings of IEEE 4th International Electrical and Energy Conference (CIEEC), 2021.}
            \item {Xinze, Zhang, Kun He, Qi Sima, and Yukun Bao. "Incremental deep universal approximiator for time series forecasting" Submitting to IEEE Transactions on Neural Networks and Learn Systems. (SCI A, IF 10.451. Preprint is coming soon.)}
            \item {Xinze, Zhang, Qi Sima, and Yukun Bao. "Dual-stage input selection of deep neural networks for time series forecasting." Submitting to IEEE Transactions on Cybernetics. (SCI A, IF 11.448. Preprint is coming soon.)}
            \item {Xinze, Zhang, Qi Sima, and Yukun Bao. "Does decoder matter in recurrent modeling framework for time series prediction? Some experimental evidences." (Working on)}
            \item {Xinze, Zhang, Zhenhua Chen, and Kun He. "Adversarial defense for neural machine translation with sparsing word embeddings." (Working on)}
            \item {张心泽, "账务智能处理中会计机器代理的研究." 华中科技大学（硕士学位论文）, 2017.}
            \item {张心泽, 蔡淑琴, 罗思宇. "基于支持向量机的在线负面口碑处理专家识别方法." 统计与决策, 2017, 22:79-83.}
        \end{cvitems}
    }
\end{cventries}